Scipion Tailored for TEM Facilities: Image Processing in Streaming

### 2018-02-28 0.abstract.tex
Renamed workflow file and fixed Scipion reference

Three dimensional electron microscopy (3DEM) is becoming a very data-intensive field in which vast amounts of experimental data are acquired at high speed. To manage such large-scale image data  projects, we have previously described  a modular workflow system called \scipion. We present here the first main extension of \scipion that allows to process data in streaming. Streaming processing allows to overlap data acquisition with the first steps of digital image processing and therefore helps to: (1) detect problems at early stages, (2) save computing time and (3) provide users with a in deep evaluation of the data quality before the data acquisition is finished. This idea of processing the data while being acquired has been implemented in different laboratories mainly using custom-made scripts. The advantages of our \scipion solution are: (1) flexibility: users can customize their workflows from a  large collection of preloaded algorithms; (2) repeatability and traceability: workflows are stored and can be re-executed later, either with the same data or a different data set; (3) monitorization: there are special utilities that constantly check how the execution of the algorithms is going and inform about possible anomalies; (4) reports: we have developed several GUIs that are updated periodically and produce a graphical summary (e.g, CTF defocus values, system load, etc). This summary may be  generated in HTML format that can be easily published though a public web-site to provide access for external users; (5) backup: both local and remote backup of the data and image processing is provided. At present, \scipion has been installed and is in production mode in three facilities. And it is being considered in several more.

>>>>

Three dimensional electron microscopy (3DEM) is becoming a very data-intensive field in which vast amounts of experimental images are acquired at high speed. To manage such large-scale projects, we have previously developed  a modular workflow system called \scipion \citep{delarosatrevin2016}. We present here a major extension of \scipion that allows stream processing of EM images while the data is being acquired. This approach helps to detect problems at early stages, saves computing time and provides users with an in deep evaluation of the data quality before the acquisition is finished. This idea has been implemented in several laboratories by using custom-made scripts. The advantages of our proposed solution are: (1) flexibility: users can customize their workflows from a  large collection of preloaded algorithms; (2) repeatability and traceability: workflows are stored and can be re-executed later, either with the same data or a different data set; (3) monitorization: there are utilities that constantly check how the execution of the algorithms is going and inform about possible anomalies; (4) reports: we have developed several graphical interfaces that are updated periodically producing a summary (e.g, CTF defocus values, system load, etc). This summary may be generated in HTML format and easily published though a public web-site to provide access for external users; (5) backup: both local and remote backup of the data and image processing is provided. At present, \scipion has been installed and is in production mode in several Cryo-EM facilities and it is being considered in many more.

### 2018-02-28 3.workflow.tex
Renamed workflow file and fixed Scipion reference

The data flow created by an electron microscope requires a careful design of the IT infrastructures.  Different facilities has adopted different solutions and therefore, 
how \scipion  access data and interchange information is very facility dependent. In this section we discuss  the different solutions applied in the different facilities in which \scipion is running.

So far, \scipion is being used routinely in four Cryo-EM facilities: \emph{Science for life Laboratory} (SciLifeLab, \url{http://www.scilifelab.se}),  \emph{European Synchrotron Radiation Facility} (ESRF, \url{http://www.esrf.eu/}), \emph{Diamond Light Source Synchrotron} (Diamond, \url{http://www.diamond.ac.uk}) and \emph{National Center for Biotechnology} (CNB, \url{http://www.cnb.csic.es}). \scipion original design satisfied the requirements of our home facility (CNB), in which \scipion automatically fetches newly recorded movies from a network mounted disk. After this first installation, \scipion was deployed on SciLifeLab (a centralized facility located at Stockholm) where a rigorous booking system is followed. There, \scipion was adapted to interface with this booking platform in order to produce better reports. Lately,  \scipion has been installed in a large synchrotron  such as ESRF and Diamond  where projects are handled by ISPyB (a customized laboratory management information system -LIMBS- \citep{Delageniere2011}) and data are saved on a distributed file system that heavily penalizes access to lists of files. In this environment, \scipion needs to constantly interchange information with ISPyB, and it cannot longer check if there is a new file in a particular storage device but must wait to be informed by the system that a new file has been created. All these particularities, that will be described in detail in the following, could only be handled thanks to a careful design that prioritizes flexibility at many levels.

@@

\input{3.workflow_cnb.tex}
\input{3.workflow_delarosa.tex}
\input{3.workflow_diamond.tex}

>>>>

The data flow created by an electron microscope requires a careful design of the IT infrastructures.  Different facilities has adopted different solutions and therefore, 
[**JMRT I don't really like how this sentence sounds. It suggest that Scipion installations are very different among facilities and this is not True, even if the initial wizard is or how folders are structured] how \scipion  access data and interchange information is very facility dependent. In this section we discuss  the different solutions applied in the different facilities in which \scipion is running.

So far, \scipion is being used routinely in four Cryo-EM facilities: \emph{Science for life Laboratory} (SciLifeLab, \url{http://www.scilifelab.se}),  \emph{European Synchrotron Radiation Facility} (ESRF, \url{http://www.esrf.eu/}), \emph{Diamond Light Source Synchrotron} (Diamond, \url{http://www.diamond.ac.uk}) and \emph{National Center for Biotechnology} (CNB, \url{http://www.cnb.csic.es}). \scipion original design satisfied the requirements of the CNB, in which \scipion automatically fetches newly recorded movies from a network mounted disk. After this first installation, \scipion was deployed on SciLifeLab (a centralized facility located at Stockholm) where a rigorous booking system is followed. There, \scipion was adapted to interface with this booking platform in order to produce better reports. Lately,  \scipion has been installed in a large synchrotron  such as ESRF and Diamond  where projects are handled by ISPyB (a customized laboratory management information system -LIMBS- \citep{Delageniere2011}) and data are saved on a distributed file system that heavily penalizes access to lists of files. In this environment, \scipion needs to constantly interchange information with ISPyB, and it cannot longer check if there is a new file in a particular storage device but must wait to be informed by the system that a new file has been created. All these particularities, that will be described in detail in the following, could only be handled thanks to a careful design that prioritizes flexibility at several levels.

@@

\input{3.workflow_cnb.tex}
\input{3.workflow_scilifelab.tex}
\input{3.workflow_diamond.tex}
